Compare pseqs

### 2019-05-27 comparepseqs.Rmd
Wrong order

```{r libraries}
library(dplyr)
library(tibble)
library(phyloseq)
library(microbiome)
library(parallel)
library(knitr)
library(gridExtra)
library(vegan)
```

@@

@@

```{r subset runs}
if (exists("subset.run")) {
    message(paste0("Subset ", subset.run))
    rds <- rds[subset.run]
}
```

@@

    if (length(missing) > 0) {
        pseq <- import_filter_data(rds[[key]] ,excluded = c("DIAB"))
        dset <- meta.merge.alphadiversity(pseq) %>%
            mutate(diversities_shannon = scale(diversities_shannon))

@@

    diversities <- mergediversities(ret[[key]][["alphadiversity"]],
                                    ret[[key]][["betadiversity"]])

    alpha.diversity.min <- plot.alpha(diversities$min, colorlimit = 0.6)
    alpha.diversity.max <- plot.alpha(diversities$max, colorlimit = 0.6)

    beta.diversity.min <- plot.beta(diversities$min)
    beta.diversity.max <- plot.beta(diversities$max)

    gs4 <- list(alpha.diversity.min$yaxis,
                alpha.diversity.min$plot,
                beta.diversity.min$plot,
                alpha.diversity.min$legend,
                alpha.diversity.min$xaxis,
                beta.diversity.min$xaxis,
                beta.diversity.min$xlab,
                text_grob("A.", size = 18),
                alpha.diversity.max$yaxis,
                alpha.diversity.max$plot,
                beta.diversity.max$plot,  
                alpha.diversity.max$xaxis,
                beta.diversity.max$xaxis,
                beta.diversity.max$xlab,
                text_grob("B.", size = 18))

@@

```{r plot alpha diversity, eval = FALSE}

alphadiversity <- readRDS("rds-comparepseqs/alpha-R16S.rds")
alphadiversity

diversity.min <- mergediversities(alpha.min, beta.min)

alpha.plot.min <- mclapply(alpha.min, function(x) { mergediversities(},
                               mc.cores = length(pseq))

gs4 <- c(list("yaxis" = alpha.plot.min[[1]]$yaxis,
              "xaxis" = alpha.plot.min[[1]]$xaxis),
              lapply(alpha.plot.min, function(x) x$plot))

g4.firstline <- c(1, seq(3, length(alpha.plot.min)+2))
g4.secondline <- c(NA, rep(2, length(alpha.plot.min)))

g4 <- arrangeGrob(grobs = gs4, layout_matrix = rbind(g4.firstline, g4.secondline))

ggsave(file = "cache/pseqdiff-alpha-min.png", plot=g4, height=6, width=9)

```

```{r join alphas, eval = FALSE}
sfx <- names(dset)
res <- alpha.min[[1]]

for(i in head(seq_along(alpha.min), -1)) {
    res <- merge(res,
                 alpha.full[[i+1]],
                 all = TRUE,
                 suffixes = paste0("_", sfx[i:(i+1)]),
                 by = c("model_name", "term", "response"))
}

res %>% colnames

res %>%
    dplyr::select(response, starts_with("estimate_"), starts_with("p.value"))

```

>>>>

```{r libraries}
library(dplyr)
library(tibble)
library(phyloseq)
library(microbiome)
library(parallel)
library(knitr)
library(gridExtra)
library(vegan)
library(ggpubr)
```

@@

Loading descriptions for clinical data

```{r variables, warning = FALSE}
names.dset <- getdescriptions()
```

@@

```{r subset runs}
if (exists("subset.run")) {
    message(paste0("Subset ", subset.run))
    rds <- rds[subset.run]
}

rds <- list("gtdb" = 1 , "centrifuge" = 2)
```

@@

    if (length(missing) > 0) {
        pseq <- import_filter_data(rds[[key]])
        dset <- meta.merge.alphadiversity(pseq) %>%
            mutate(diversities_shannon = scale(diversities_shannon))

@@

    diversities <- mergediversities(ret[[key]][["alphadiversity"]],
                                    ret[[key]][["betadiversity"]])
diversities$min
    alpha.diversity.min <- plot.alpha(diversities$min, colorlimit = 0.6)
    alpha.diversity.full <- plot.alpha(diversities$full, colorlimit = 0.6)

    beta.diversity.min <- plot.beta(diversities$min)
    beta.diversity.full <- plot.beta(diversities$full)

    gs4 <- list(alpha.diversity.min$yaxis,
                alpha.diversity.min$plot,
                beta.diversity.min$plot,
                alpha.diversity.min$legend,
                alpha.diversity.min$xaxis,
                beta.diversity.min$xaxis,
                beta.diversity.min$xlab,
                text_grob(paste("A.", key), size = 18, just = "left"),
                alpha.diversity.full$yaxis,
                alpha.diversity.full$plot,
                beta.diversity.full$plot,  
                alpha.diversity.full$xaxis,
                beta.diversity.full$xaxis,
                beta.diversity.full$xlab,
                text_grob(paste("B.", key), size = 18, just = "left"))

@@

```{r plot alpha diversity, eval = FALSE}
g <- arrangeGrob(plotlist[[1]], plotlist[[2]], ncol=1)
ggsave(file="cache/plotlist.pdf", g, height=6*length(plotlist), width=10)
```

```{r debug, eval = FALSE}
ret[["centrifuge"]]$betadiversity$full$model_1
```
